AFQ-Insight

### 2019-12-19 reports/manuscript/sections/conclusion.tex
Add zenodo DOI

The method is packaged as open-source software called AFQ-Insight
that is openly available, and provides a clear API to allow
for extensions of the method. The sofware integrates within a
broader automated fiber quantification software ecosystem: AFQ
\cite{yeatman2012tract}, which extracts tractometry data from raw and
processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use
of the software, the results presented in this paper are also provided
in \url{https://github.com/richford/afq-insight-paper} as a series of
Jupyter notebooks \cite{kluyver2016jupyter}.

>>>>

The method is packaged as open-source software called AFQ-Insight
that is openly available, and provides a clear API to allow
for extensions of the method. The sofware integrates within a
broader automated fiber quantification software ecosystem: AFQ
\cite{yeatman2012tract}, which extracts tractometry data from raw and
processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use
of the software, the results presented
in this paper are also provided in
\url{https://github.com/richford/AFQ-Insight/tree/master/examples/preprint-notebooks} as a series of Jupyter notebooks
\cite{kluyver2016jupyter}.
